%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{pratham-resume-openfont}
\usepackage{fancyhdr}
\usepackage{color}
\definecolor{light}{rgb}{0.5, 0.5, 0.5}
\def\light#1{{\color{light}#1}}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Pratham}{Goyal}{ \urlstyle{same}\href{https://prathamgoyal.com}{prathamgoyal.com}\\\
\href{mailto:contact@prathamgoyal}{contact@prathamgoyal.com} | +1 250.879.3123
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.34\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}
\subsection{Thompson Rivers \\ University} 
\descript{Diploma in Computing~~ Science}
\location{Grad. Sept 2022 | Kamloops, BC}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
LinkedIn://  \href{https://www.linkedin.com/in/prathamgoyal}{\bf prathamgoyal} \\
Github:// \href{https://github.com/Pratham9}{\bf Pratham9} \\
Twitter: // \href{https://twitter.com/GoreKehnePerry}{\bf goyalperry}
\sectionsep



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\location{Expert:}
Active Directory \textbullet{} Azure AD \textbullet{} PowerShell \\
\textbullet{} ITSM Administration \textbullet{} Microsoft 365 \textbullet{}\\ 
 FreshService \textbullet{} Apple Configurator 2 \\
\textbullet{} Intune MDM \textbullet{} Meraki Cloud Dashboard 
 SharePoint Online \textbullet{} Exchange Online \\
\ \textbullet{} AI Integration (ChatGPT, Copilot, Perplexity, etc.)\\
\location{Confident:}
C\# \textbullet{} Python \textbullet{} PHP \textbullet{} MySQL \textbullet{} JavaScript  \\
\textbullet{} PowerApps \textbullet{} Server Manager \textbullet{} \\
Datto RMM \textbullet{} Autotask PSA \textbullet{} IT Glue \\ 
\textbullet{} Office Apps \\
\location{Familiar:}
Sage \textbullet{} Networks (Sophos, Meraki, Cisco AnyConnect, OpenVPN) \textbullet{} MDT \textbullet{} RDS \\
\textbullet{} Basic Understanding of Machine Learning Concepts \textbullet{} MS Project \\
\sectionsep

\section{Additional Info}
\textbullet{} Volunteered for United Way Campaign and helped paint the local Food Hub Project Storefront. \\
\textbullet{} Organized the Global Game Jam for the 3rd time at TRU which involved getting funding, {\bf event planning}, and execution. \\
\textbullet{} Promoted to {\bf President} of the {\bf Game Development Club} and set up a board to advance club activities. \\
\textbullet{} Currently preparing for {\bf AWS Certified Developer} Associate. \\
\textbullet{} Actively learning and applying AI technologies, with a focus on ChatGPT and prompt engineering, to develop innovative solutions and automate processes. This engagement enhances efficiency, creativity, and the ability to tailor AI responses in technical projects.
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.65\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\subsection{TLC Solutions}
\descript{Service Technician}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Delivered frontline technical support, achieving top-tier problem-solving effectiveness and customer satisfaction, evidenced by a {\bf 100\% Kill Rate} and consistently positive CSAT feedback.
\item Orchestrated iPad setup and management using {\bf Mac, Apple Configurator 2,} and {\bf Intune MDM;} streamlined provisioning and enforced device restrictions, significantly enhancing operational efficiency and security.
\item Developed and executed {\bf PowerShell scripts} for critical security and administrative tasks, doubling efficiency in administrative operations and enhancing the organization's security posture.
\item Improved response times by over {\bf 50\%}, demonstrating a steadfast commitment to enhancing service responsiveness and client communication.
\end{tightemize}
\sectionsep

\subsection{The Dawson Group}
\descript{Systems Administrator \light{| Jan 2022 - Sept 2022 | Kamloops, BC}} 
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Piloted an employee onboarding system which on implementation will be a better experience for support services and new employees, made Project Charter, {\bf Documentation}, and got Stakeholder acceptance via Showcase of a {\bf Technical Demo}.
\item Streamlined ITSM system integration and boosted team productivity by automating IT onboards with {\bf PowerShell scripting}, FreshService features, and {\bf Python}, effectively resolving bugs and ensuring a smooth transition to production with optimized code. This initiative saved over {\bf 200 hours} annually.
\item Implemented a data manipulation pipeline and cleanup query using {\bf Power Query saving 4 hours each week} for the Payroll team.
\item Led the {\bf Employee Onboarding Automation} project, significantly enhancing the onboarding process. Utilized {\bf PowerShell, FreshService, Active Directory,} and {\bf Azure AD} to automate account creation within 60 seconds post-approval, achieving {\bf 30-minute savings} per onboard and reducing errors.

\end{tightemize}
\sectionsep

\descript{IT Support Technician \light{| Sept 2021 - Dec 2021 | Kamloops, BC}}
\begin{tightemize}
\item Functioned as the first point of contact for users’ technical problems as the primary onsite and {\bf remote support technician} for a medium size organization.
\item Administered ITSM/ticketing system, {\bf Azure/Active Directories}, VoIP Console, Digital Signage, and managed Mobility Portal. Used to {\bf resolve user problems} and enabled people across the organization to work better.
\item Supported Information Technology operations within the organization by {\bf providing service, maintaining, refurbishing, and building} PCs, workstations, and mobility devices.
\end{tightemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Technical Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\sectionsep

\end{minipage} 

\end{document}
\documentclass[]{article}