%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{pratham-resume-openfont}
\usepackage{fancyhdr}
\usepackage{datetime}

\newcommand{\jobtitle}{Computer Technician }
\newcommand{\companyname}{Kamloops Computer Centre}
\pagestyle{fancy}
\fancyhf{}
\date{\today}
\begin{document}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Pratham}{Goyal}{ \urlstyle{same}{prathamgoyal.com}\\\
{goyalp09@pm.me} | +1 250.879.3123
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\sectionsep

\section{}
\location{\today}

\sectionsep
\sectionsep

\descript{\companyname}
\location{945 Notre Dame Drive,} 
\location{Kamloops, B.C. V2C 5N9} 

\sectionsep
\sectionsep

\descript{RE: \jobtitle}

\sectionsep
\sectionsep

\descript{Dear Ryan,} 

\sectionsep

\location{I am writing to apply for the \jobtitle role at \companyname. I am excited about the opportunity to join your team and contribute my skills and experience in IT support and automation.}

\sectionsep

\begin{tightemize}
    \item \location{As a Systems Administrator, I have a proven track record of boosting team productivity and implementing solutions that save time and improve efficiency. For example, I was able to save 200 hours per year for my team by automating IT onboards using FreshService features, PowerShell, and Python. Additionally, I implemented a data manipulation pipeline using Power Query that saved 4 hours per week for the Payroll team.} 
    \item \location{I am also skilled at piloting and implementing new systems and processes. I recently led the development of an employee onboarding system that will improve the experience for support services and new employees. I created a Project Charter, documentation, and a technical demo to showcase the system to stakeholders, and I was able to secure their approval to move forward with the project.}
    \item \location{In addition to my experience in automation and project management, I am also proficient in providing IT support to users. As an IT Support Technician, I was the primary onsite and remote support technician for a medium-sized organization. I was responsible for administering the ITSM/ticketing system, Azure/Active Directories, and other tools to resolve user problems and enable people across the organization to work better. I also supported the organization's IT operations by providing service, maintaining, refurbishing, and building PCs, workstations, and mobility devices.}
    \item \location{Finally, I have experience in implementing security solutions and training vulnerable employees. I conducted a phishing simulation and set up security awareness training for employees, which resulted in a decrease in phish-prone users by 85\%.}
\end{tightemize}

\sectionsep

\location{Overall, I believe that my skills and experience make me an excellent fit for the \jobtitle role at \companyname. I am eager to learn more about the position and how I can contribute to your team. Thank you for considering my application.} 
\sectionsep

\location{Sincerely,} 

\sectionsep
\sectionsep
\sectionsep
\sectionsep 
\sectionsep
\sectionsep
\sectionsep
\sectionsep
\sectionsep
\sectionsep
\sectionsep
\sectionsep
\sectionsep

\descript{Pratham Goyal}

\end{document}  \documentclass[]{article}