%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{pratham-resume-openfont}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Pratham}{Goyal}{ \urlstyle{same}\href{http://prathamgoyal.me}{prathamgoyal.me}\\\
\href{mailto:goyalp09@pm.me}{goyalp09@pm.me} | +1 250.879.3123
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.34\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{Thompson Rivers}
\subsection{University}
\descript{Diploma in Computer Science}
\location{Grad. Sept 2022 | Kamloops, BC}
\sectionsep

\subsection{Rukhmani Devi Sr.}
\subsection{Secondary Collegiate}
\location{Grad. May 2017 |  Patiala, India}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github:// \href{https://https://github.com/Pratham9}{\bf Pratham9} \\
LinkedIn://  \href{https://www.linkedin.com/in/prathamgoyal}{\bf prathamgoyal} \\
Itch.io: // \href{https://oto-san.itch.io/}{\bf Oto-san} \\
Twitter: // \href{https://twitter.com/GoreKehnePerry}{\bf goyalperry}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{Undergraduate}
Data Structures and Algorithms \\
Software Architecture \& Design\\
Game Design \& Development* \\
Advanced Web Design \& Programming* \\
Mobile App Development* \\
Human-Computer Interaction \\
Database Systems \\
Career Management \\
{\footnotesize \textit{\textbf{(Teaching Asst *) }}} \\

\sectionsep
\subsection{Post-Graduate}
Full-Time Game Dev - Thomas Brush \\
Complete C\# Masterclass - Denis Panjuta \\
Introduction to C\# Programming \& Unity \\
 - University of Colorado System \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\location{Expert:}
C\# \textbullet{} Java \textbullet{} PowerShell \textbullet{} Googling \\ 
\location{Confident:}
C \textbullet{} Python \textbullet{} CSS \textbullet{} PHP \textbullet{} MySQL \\ \textbullet{} JavaScript \\
\location{Familiar:}
Dart \textbullet{} Android 
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.65\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{The Dawson Group}
\descript{| Systems Administrator }
\location{Jan 2022 - Sept 2022 | Kamloops, BC}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Boosted team productivity {\bf saving 200 hours} a year via automation of IT onboards using FreshService features, {\bf PowerShell}, and {\bf Python}. 
\item Implemented a data manipulation pipeline and cleanup query using {\bf Power Query saving 4 hours each week} for the Payroll team.
\item Piloted an employee onboarding system which on implementation will be a better experience for support services and new employees, made Project Charter, {\bf Documentation}, and got Stakeholder acceptance via Showcase of a {\bf Technical Demo}.
\item Conducted phishing simulation and set up {\bf security awareness training} for vulnerable employees, leading to a decrease in phish-prone users by {\bf 85\%}.
\item Administered ITSM/ticketing system, {\bf Azure/Active Directories}, VoIP Console, Digital Signage, and managed Mobility Portal. Used to {\bf resolve user problems} and enabled people across the organization to work better.
\end{tightemize}
\sectionsep

\runsubsection{Bubble Time Tea \& Cafe}
\descript{|  Website Technology Consultant }
\location{Jan 2021 – Apr 2021 | Kamloops, BC}
\begin{tightemize}
\item Worked on a high-fidelity website {\bf Proof of Concept} in {\bf HTML, CSS, Bootstrap, and JavaScript} for online business identity with online ordering support.
\item Implemented a Web application, Deployed using {\bf Git}.io to enabled user accounts login via {\bf MySQL} back-end.
\item Conducted usability testing and {\bf Optimized User Interface} for mobile devices improving by {\bf 70\%} over original design.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Technical Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Technical Projects}
\runsubsection{MetaMorphing}
\descript{| Design \& Development Lead}
\location{Oct 2022 – Present}
Taking my first step into the world of indie game development with this Project.
\begin{tightemize}
    \item Tools: {\bf Unity}, Blender, Audacity, GIMP, Trello, GitKraken, {\bf Visual Studio}
    \item 3D Game with a goal to build a self-sustaining system by upgrading/ terraforming the planet, while dealing with external dangers of the universe.
\end{tightemize}
\sectionsep

\runsubsection{Bubblerio}
\descript{| Technical Lead}
\location{Sept 2020 – Dec 2020}
\begin{tightemize}
    \item {\bf Technical Lead} for a team of four, tasked to make a theme-based game for the final project of the {\bf game development} course. Fast-paced 2D precision platformer inspired by Celeste and Hollow Knight created in {\bf Unity} using {\bf C\#}.
    \item Designed levels, implemented player mechanics, and optimized playability. Also added enemies coded using {\bf pathfinding algorithms} in {\bf C\#}.
    \item Used {\bf scrum agile methodology}, daily morning stand-ups, weekly sprint planning, and sprint review and retrospective.
    \item Source Control Managed using {\bf GitHub} \& Project management using Trello.
\end{tightemize}  
\sectionsep

\end{minipage} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Additional Information
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Additional Information}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
    \item Volunteered for United Way Campaign and helped paint the local Food Hub Project Storefront.
    \item Organized the Global Game Jam for the 3rd time at TRU which involved getting funding, {\bf event planning}, and execution.
    \item Promoted to {\bf President} of the {\bf Game Development Club} and set up a board to advance club activities.
    \item Currently preparing for {\bf AWS Certified Developer} Associate.
\end{tightemize}

\end{document}  \documentclass[]{article}