%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{pratham-resume-openfont}
\usepackage{fancyhdr}
\usepackage{datetime}
 
\pagestyle{fancy}
\fancyhf{}
\date{\today}
\begin{document}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Pratham}{Goyal}{ \urlstyle{same}\href{http://prathamgoyal.me}{prathamgoyal.com}\\\
\href{mailto:goyalp09@pm.me}{goyalp09@pm.me} | +1 250.879.3123
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\sectionsep

\section{}
\location{\today}

\sectionsep
\sectionsep

\descript{Electronic Arts Canada}
\location{330 Sanderson Way,} 
\location{Burnaby, BC V5G 4X1} 

\sectionsep
\sectionsep

\descript{RE: Software Engineer - C\# \& WPF - Frostbite}

\sectionsep
\sectionsep

\descript{Dear Hiring Manager,} 

\sectionsep

\location{The 9-year-old Pratham had one dream: to go to space. While I was fascinated by the innovations in the field of physics, I found my passion in computers due to the creative freedom that they granted, and I pursued further education to learn more about them. I am thrilled to apply in the Frostbite Team at Electronic Arts, since not only does it allow me to be a part of a world leader in interactive experiences impacting billions of users, but it also allows me to inclusively contribute alongside a team of experts with values that align with my goals, allowing me to turn dreams into shared experiences. }

\sectionsep

\begin{tightemize}
    \item \location{As a recent graduate from The Thompson Rivers in Computing Science I have experience in writing code, testing applications, and debugging software from the knowledge acquired in my coursework.} 
    \item \location{I also have experience working with various programming languages, such as C\#, Java, and Python. I enjoy problem solving and keep my skills sharp by practicing challenging questions.}
    \item \location{In addition, I have a strong understanding of software development methodologies, such as MVC Framework, Agile, and Waterfall from the projects that I lead. }
    \item \location{Having lead multiple group projects I understand what it means to lead people, and have developed my skills in communication, strategic-planning, decision making, analytical thinking, and delegation of tasks. }
\end{tightemize}

\sectionsep

\location{I am a motivated individual who is always eager to learn new things. My experience and skills have allowed me to develop a keen eye for detail, which is essential for solving complex problems. I am confident that I could be a valuable asset to your team and contribute to the success of your company. I look forward to discussing my qualifications and experience with you further. Thank you for your time and consideration.} 
\sectionsep

\location{Sincerely,} 

\sectionsep
\sectionsep
\sectionsep
\sectionsep 
\sectionsep
\sectionsep
\sectionsep
\sectionsep
\sectionsep
\sectionsep
\sectionsep
\sectionsep
\sectionsep

\descript{Pratham Goyal}

\end{document}  \documentclass[]{article}